Paper figures

### 2019-01-07 paper_figures.Rmd
added panel

---
title: "Paper figures"
author: "Francesco Beghini"
date: "January 6, 2019"
output: html_document
---

@@

source('R/loadQiimeData.R')
```

@@

pds_genus <- phyloseq_to_deseq2(ggtopi_subs.genus, design =  ~ timepoint + timepoint:real_vaccine + timepoint:real_bifido + timepoint:real_vaccine:real_bifido, ignoreRank = TRUE)
dds_genus <- DESeq2::DESeq(pds_genus, parallel = TRUE, quiet = TRUE, full = mmtx)
```
## Panel E: Boxplot of abundance of significant genera from DESeq2 differential analysis
```{r}
res37 <- DESeq2::results(dds_genus, name = "timepointT7", alpha = 0.05)
res37.filt <- res37[!is.na(res37$padj),]
res37.filt <- res37.filt[res37.filt$padj<0.05,]

@@

genus_ab_t %>%

  bind_cols(data.frame(tax_table(ggtopi_subs.genus.relab)[genus_ab_t$OTU,c('Phylum','Family','Genus')])) %>%
ggplot() +
  geom_boxplot(aes(reorder(interaction(Family, Genus), Abundance, FUN = median), Abundance, fill=timepoint)) + 
  facet_grid(Phylum ~ ., scales = "free", space = "free_y", as.table= T)+
  coord_flip() + 
  theme(strip.background = element_rect(colour = "transparent", fill = "transparent"),
      strip.text.y = element_text(angle = 0))

>>>>

---
title: "Paper figures"
author: "Francesco Beghini"
date: "January 6, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

source('R/loadQiimeData.R')
source('R/ggtheme.R')
```

@@

pds_genus <- phyloseq_to_deseq2(ggtopi_subs.genus, design =  ~ timepoint + timepoint:real_vaccine + timepoint:real_bifido + timepoint:real_vaccine:real_bifido, ignoreRank = TRUE)
dds_genus <- DESeq2::DESeq(pds_genus, parallel = TRUE, quiet = TRUE, full = mmtx)
```

## Panel E: Boxplot of abundance of significant genera from DESeq2 differential analysis. Genera with median below 1% are filtered
```{r}
res37 <- DESeq2::results(dds_genus, name = "timepointT7", alpha = 0.05)
res37.filt <- res37[!is.na(res37$padj),]
res37.filt <- res37.filt[res37.filt$padj<0.05,]

@@

genus_ab_t %>%
  bind_cols(data.frame(tax_table(ggtopi_subs.genus.relab)[genus_ab_t$OTU,c('Phylum','Family','Genus')])) %>%
  filter(OTU %in% (genus_ab_t %>%
  group_by(OTU, timepoint) %>%
  summarise(median=median(Abundance)) %>%
  group_by(OTU) %>%
  summarise(filt=min(median)>0.01) %>% filter(filt==TRUE))$OTU) %>%
  filter(Phylum != "Unassigned") %>%
  mutate(taxlab = ifelse(stringr::str_detect(Genus,'uncultured'), paste('Uncultured',Family,sep = ' '), paste(Genus))) %>%
ggplot() +
  geom_boxplot(aes(reorder(taxlab, Abundance, FUN = median), Abundance, fill=timepoint)) +
  facet_grid(Phylum ~ ., scales = "free", space = "free_y", as.table= T) +
  scale_fill_brewer(name = "Timepoint", palette="Dark2") +
  coord_flip() +
  xlab('') +
  ylab("Relative abundance") +
  theme_cm()
```

## Panel F: Abundance of Bacteroidales 24/7 and Lachnospiraceae NK4A136 through timepoints and treatment
```{r}
idx_247 <- which(tax_table(gg_topi.genus.relab)[,'Family'] == "Bacteroidales S24-7 group" & tax_table(gg_topi.genus.relab)[,'Genus'] == "uncultured bacterium")
idx_lachno <- which(tax_table(gg_topi.genus.relab)[,'Genus'] == "Lachnospiraceae NK4A136 group" )

otu_table(gg_topi.genus.relab)[c(idx_247,idx_lachno),] %>%
  data.frame %>%
  tibble::rownames_to_column("OTU") %>%
  tidyr::gather_("SampleID", "Abundance", setdiff(colnames(.), "OTU")) %>%
  mutate(timepoint=stringr::str_sub(.$SampleID,12, 13)) %>%
  mutate(condition= stringr::str_sub(.$SampleID,4, 6)) %>%
  bind_cols(data.frame(tax_table(gg_topi.genus.relab)[.$OTU,c('Phylum','Family','Genus')])) %>%
  mutate(taxlab = ifelse(stringr::str_detect(Genus,'uncultured'), paste('Uncultured',Family,sep = ' '), paste(Genus))) %>%
  ggplot() +
  geom_boxplot(aes(timepoint, Abundance, fill=condition)) +
  scale_fill_brewer(name = "Timepoint", palette="Dark2") +
  facet_grid(taxlab ~ ., scales = "free", space = "free_x", as.table= T) +
  theme_cm()
```
